% Final HCI Evaluation Report (LaTeX)
% Generated on 2025-09-09
\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{caption}
\usepackage{float}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}

\newcommand{\sev}[1]{\textbf{#1}} % severity macro
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\title{NityMulya Usability Evaluation\\\large Heuristic Evaluation (HE) and Cognitive Walkthrough (CW)}
\author{Project Team (SDP Group)\\Course: Human--Computer Interaction}
\date{2025-09-09}

\begin{document}
\maketitle
\tableofcontents
\newpage

% --------------------------------------------------
% 1. System Overview (from 01_system_overview.md)
% --------------------------------------------------
\section{System Overview}
\subsection{Purpose}
NityMulya enables transparent local commerce and consumer protection through multi-role interaction (Customer, Shop Owner, Wholesaler, DNCRP Admin).

\subsection{Primary User Groups}
\begin{itemize}[leftmargin=*]
  \item \textbf{Customers}: Price lookup, shop discovery, complaints, reviews, favorites.
  \item \textbf{Shop Owners}: Inventory and order management, communication with suppliers.
  \item \textbf{Wholesalers}: Supply management, offers, restock negotiation.
  \item \textbf{DNCRP Admin}: Oversight of complaints (regulatory demo).
\end{itemize}

\subsection{Core Functional Domains}
\begin{longtable}{@{}L{3cm}L{11cm}@{}}
\toprule
\textbf{Domain} & \textbf{Key Functions}\\\midrule
Pricing & Daily pricelist, (planned) government baseline tagging \\
Inventory & CRUD for products (shop \& wholesale) + low stock alerts \\
Orders & Customer orders; owner fulfillment lifecycle \\
Complaints & Submission with evidence (media pipeline pending) \\
Reviews & Product + shop ratings, aggregation (no media yet) \\
Chat & Real-time style supply chain messaging (polling-based) \\
Geolocation & Nearby verified shops display \\
Rewards (Planned) & VAT honesty incentive logic \\
\bottomrule
\end{longtable}

\subsection{Technology Stack}
Frontend: Flutter (Dart), SharedPreferences, Geolocator, HTTP.\\
Backend: Bun + TypeScript (Hono), Postgres, JWT.\\
Data: Mix of role-specific tables + unified user schema variant in SQL assets.

\subsection{Key Constraints}
\begin{itemize}[leftmargin=*]
  \item Password hashing absent (risk).
  \item Large monolithic UI classes impede scalability.
  \item Media upload server parsing incomplete.
  \item Route duplication (complaints) and inconsistent naming conventions.
\end{itemize}

\subsection{Assumptions for Evaluation}
\begin{itemize}[leftmargin=*]
  \item Evaluated using current branch code (no production telemetry).
  \item Government price ingestion assumed not fully implemented (future feature).
  \item Review and complaint volumes moderate (no stress conditions modeled).
\end{itemize}

% --------------------------------------------------
% 2. Heuristic Evaluation (from 02_heuristic_evaluation.md)
% --------------------------------------------------
\section{Heuristic Evaluation}
Evaluator count: 4. Method: Independent review \textrightarrow{} consolidation workshop \textrightarrow{} severity assignment (highest credible severity kept).\\
Severity scale: 0 None, 1 Cosmetic, 2 Minor, 3 Major, 4 Critical.

\subsection{Issue Table}
\setlength{\tabcolsep}{4pt}
\begin{longtable}{@{}L{1.1cm}L{2.3cm}L{1.2cm}L{4.2cm}L{0.9cm}L{2.2cm}L{3.3cm}@{}}
\toprule
\textbf{ID} & \textbf{Context} & \textbf{H} & \textbf{Description} & \textbf{Sev} & \textbf{Rationale} & \textbf{Recommendation}\\\midrule
H1-1 & Complaint Submission & H1 & No upload progress indicator & 3 & Double-submit risk & Add progress bar + disable submit \\
H1-2 & Inventory Save & H1 & Silent delay on update & 2 & Unresponsiveness & Inline saving spinner + toast \\
H1-3 & Login & H1 & No loader on slow network & 2 & Retry uncertainty & Minimal skeleton/loader \\
H2-1 & Multi-role Labels & H2 & Mixed Bengali/English & 2 & Switching cost & Introduce localization \\
H2-2 & Complaint Categories & H2 & Terms unexplained & 2 & Misclassification & Helper tooltips \\
H3-1 & Complaint Form Exit & H3 & Back discards data & 3 & Data loss & Discard dialog + autosave \\
H3-2 & Inventory Edit & H3 & No undo after change & 2 & Error propagation & Undo snackbar \\
H3-3 & Order Cancellation & H3 & No confirmation & 2 & Accidental action & Confirm dialog \\
H4-1 & Role Strings & H4 & Inconsistent naming & 3 & Mental model drift & Centralize constants \\
H4-2 & Date Formats & H4 & Mixed ISO/local & 2 & Parsing confusion & Standardize formatter \\
H4-3 & Button Styling & H4 & Inconsistent hierarchy & 2 & Diluted visual cues & Theme tokens \\
H4-4 & Complaint Routes & H4 & Duplicate definitions & 3 & Maintenance risk & Deduplicate + test \\
H5-1 & Password Storage & H5 & Plaintext logic & 4 & Security flaw & Implement bcrypt + migration \\
H5-2 & Offer Submission & H5 & Duplicate taps allowed & 2 & Data noise & Disable on submit \\
H5-3 & File Validation & H5 & No type/size check & 3 & Malicious upload risk & Whitelist + size limit \\
H6-1 & Location Capture & H6 & Re-enter after denial & 2 & Redundant input & Cache last known \\
H6-2 & Gov Price Ref & H6 & Must recall baseline & 2 & Cognitive load & Readonly official field \\
H7-1 & Inventory Bulk & H7 & No batch update & 2 & Slow for catalog & Batch editor \\
H7-2 & Saved Filters & H7 & Filters reset & 2 & Repetitive steps & Persist per tab \\
H8-1 & Dashboard Density & H8 & Overloaded stats & 2 & Scan difficulty & Subview segmentation \\
H8-2 & Typography & H8 & Inconsistent scale & 2 & Visual noise & Apply scale ramp \\
H9-1 & Network Errors & H9 & Generic message & 2 & No recovery guidance & Retry CTA \\
H9-2 & Price Fetch Fail & H9 & No cached fallback & 3 & Trust erosion & Cache last payload \\
H9-3 & Complaint Fail & H9 & Form cleared & 3 & Re-entry burden & Retain form state \\
H10-1 & Complaint Evidence & H10 & No file guidance & 2 & Trial-and-error & Inline microcopy \\
H10-2 & Review Ratings & H10 & No scale explanation & 1 & Minor clarity & Tooltip / info icon \\
\bottomrule
\end{longtable}

\subsection{Prioritized Fix Batch (Sprint 1)}
1) H5-1 (bcrypt) \quad 2) H1-1 + H5-3 (upload robustness) \quad 3) H3-1 (draft persistence) \quad 4) H4-1 (taxonomy) \quad 5) H9-2 (pricing cache)

% --------------------------------------------------
% 3. Cognitive Walkthrough (from 03_cognitive_walkthrough.md)
% --------------------------------------------------
\section{Cognitive Walkthrough}
Three representative tasks (first-time user lens) assessed action sequences, expected system feedback, and potential breakdowns.

\subsection{Tasks}
\begin{longtable}{@{}L{1.2cm}L{2.5cm}L{6.5cm}L{5cm}@{}}
\toprule
\textbf{ID} & \textbf{Role} & \textbf{Goal} & \textbf{Success Criteria}\\\midrule
T1 & Customer & Submit complaint with photo evidence for nearby shop product issue & Complaint ID returned and visible in list \\
T2 & Shop Owner & Update product stock using government price reference & Quantity saved; inventory reflects change \\
T3 & Wholesaler & Identify low-stock shop and send restock offer & Offer acknowledged / appears in offers list \\
\bottomrule
\end{longtable}

\subsection{Representative Step Extract}
\begin{longtable}{@{}L{0.6cm}L{0.6cm}L{3.4cm}L{3.4cm}L{2.6cm}L{1.1cm}L{3.4cm}@{}}
\toprule
\textbf{T} & \textbf{#} & \textbf{Action} & \textbf{Expected} & \textbf{Observed} & \textbf{Break?} & \textbf{Recommendation}\\\midrule
T1 & 1 & Open app \& login & Dashboard loads & Works & No & Preload session if token valid \\
T1 & 7 & Attach photo & Show upload progress & No progress shown & Yes & Progress bar + size limit \\
T1 & 9 & Submit complaint & Spinner + success ref & Delay, no spinner & Yes & Unified async overlay \\
T1 & 10 & Return to list & New complaint visible & Needs manual refresh & Yes & Optimistic add + auto refresh \\
T2 & 6 & Save changes & Confirmation & Silent & Yes & Toast ``Saved'' \\
T2 & 7 & Cross-check gov price & Readonly field & Not present & Yes & Show official price field \\
T3 & 8 & Send offer & Confirmation + list update & Needs refresh & Yes & Optimistic insertion \\
\bottomrule
\end{longtable}

\subsection{Breakdown Themes}
Feedback absence; missing persistent filters; lack of government price reference; manual refresh patterns.

\subsection{Key Improvements}
Attachment progress; optimistic updates; official price field; auto-refresh; draft retention.

% --------------------------------------------------
% 4. Comparative Analysis (from 04_comparative_analysis.md)
% --------------------------------------------------
\section{Comparative Analysis (HE vs CW)}
\subsection{Issue Overlap Matrix}
\begin{longtable}{@{}L{3.2cm}L{3cm}L{4.2cm}L{3cm}@{}}
\toprule
\textbf{Category} & \textbf{HE Only} & \textbf{CW Only} & \textbf{Both}\\\midrule
Feedback / Visibility & Route duplication (structural) & Optimistic refresh, upload progress context (3) & 3 shared feedback issues \\
Security & Plaintext password & -- & -- \\
Consistency & Naming, date, buttons (3) & -- & Role labeling surfaced \\
Error Recovery & Cache, generic errors (2) & Lost form state, manual refresh (2) & 1 shared recovery item \\
Efficiency & Bulk ops, filters (2) & Distance context (1) & 1 shared efficiency issue \\
\bottomrule
\end{longtable}

HE surfaced architectural / systemic risks; CW revealed sequential, context-sensitive friction. Overlap (~30\%) indicates complementary value.

% --------------------------------------------------
% 5. Design Recommendations (from 05_design_recommendations.md)
% --------------------------------------------------
\section{Design Recommendations \& Strategy}
\subsection{Prioritized Backlog}
\begin{longtable}{@{}L{0.7cm}L{3cm}L{0.9cm}L{1.3cm}L{1cm}L{7cm}@{}}
\toprule
\textbf{Ref} & \textbf{Linked Issues} & \textbf{Sprint} & \textbf{Effort} & \textbf{Impact} & \textbf{Description}\\\midrule
R1 & H5-1 & S1 & 2d & High & Implement bcrypt + migration script + rehash existing records \\
R2 & H1-1,H1-3,H2-2,H3-1,H9-3 & S1 & 3d & High & Unified async UX kit (LoadingOverlay, Toaster, DraftCache) \\
R3 & H4-1,H4-2,H4-3 & S1 & 2d & Med & Taxonomy + design token standardization \\
R4 & H9-2 & S2 & 1.5d & Med & Local price cache \& stale indicator \\
R5 & H1-2,H7-2,H8-1 & S2 & 3d & Med & Dashboard decomposition + persistent filters \\
R6 & H3-2,H7-1 & S2 & 2d & Med & Undo \& bulk inventory operations \\
R7 & CW T2 S7 & S3 & 1d & Med & Official price reference field integration \\
R8 & H5-3,CW T1 S7 & S3 & 2d & High & Robust media pipeline (validation + progress) \\
R9 & H6-1 & S3 & 1d & Low & Last-known location reuse logic \\
R10 & CW T3 S8 & S4 & 2d & Med & Order / supply event timeline model \\
\bottomrule
\end{longtable}

\subsection{Architectural Enhancements}
Provider / Riverpod state partitioning; central API client (interceptors: auth renewal, logging, exponential backoff); event bus or WebSocket for real-time updates; modularized feature directories.

\subsection{Security Hardening Plan}
\begin{enumerate}[leftmargin=*]
  \item Bcrypt hashing \& minimum password policy.
  \item Token expiry (short) + refresh mechanism.
  \item Standard error envelope (no stack traces).
  \item Upload sanitization \& MIME validation.
\end{enumerate}

\subsection{Metrics to Track}
Complaint submission completion rate; inventory update task time; duplicate submission rate; offer response latency; crash/error frequency per 1K sessions.

\subsection{Team Contribution (Narrative)}
Security focus (Evaluator A), form resilience (Evaluator B), consistency \& taxonomy (Evaluator C), feedback timing (Evaluator D). Backlog shaped through consolidation.

\subsection{Limitations and Future Work}
No production analytics yet; media pipeline assumed; future: accessibility audit, internationalization framework, regression test harness.

% --------------------------------------------------
% End Matter
% --------------------------------------------------
\section*{Appendix (Optional References)}
Raw evaluator CSVs and consolidated findings maintained alongside this report (see repository \texttt{assignment/} directory).

\end{document}
